---
title: "Getting Started with Binomial"
author: "Ganesh Muthu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial

The package `"binomial"` is a package that allows a user to work 
with the binomial distribution, create binomial random variables, and get several useful statistics from it.

### Generating a Binomial Variable

```{r var}
binomialVar = bin_variable(trials = 5, prob = .4)
```

### Printing a Binomial Variable

```{r print}
print(binomialVar)
```

### Summarizing a Binomial Variable

```{r summary}
summary(binomialVar)
```

### Getting Binomial Statistics without a Binomial Variable
```{r stats}
bin_mean(trials = 5, prob = .4)
bin_variance(trials = 5, prob = .4)
bin_mode(trials = 5, prob = .4)
bin_skewness(trials = 5, prob = .4)
bin_kurtosis(trials = 5, prob = .4)
```

### Combination Calculator

```{r combo}
#5 choose 2
bin_choose(n = 5, k = 2)
```

### Probability Calculator

```{r prob}
#Probability of 2 successes in 5 trials with a 50% chance of success
bin_probability(success = 2, trials = 5, prob = .5)
```

### Generating Binomial Distribution

```{r dist, warning=FALSE}
bin_distribution(5, 0.5)
```

### Plotting a Binomial Distribution

```{r distP, warning=FALSE}
x = bin_distribution(5, 0.5)
plot(x)
```

### Generating a Cumulative Binomial Distribution

```{r dist2, warning=FALSE}
bin_cumulative(5, 0.5)
```

### Plotting a Cumulative Binomial Distribution

```{r distP2, warning=FALSE}
y = bin_cumulative(5, 0.5)
plot(y)
```




